\begin{plainchp}{Preface}
    \setcounter{page}{1}
    \addcontentsline{toc}{chapter}{Preface}
    \begin{refsection}
    My interest in laser-thermal propulsion began long before I started this master's thesis. It was in fact my introduction to academia, through an undergraduate research experience. This experience proved to be quite successful, as it led to my first journal publication in 2022, which demonstrated the potential of this concept for rapid-transit missions to Mars.
    
    By that point, I had already begun my master's degree at TU Delft, in search of new fields of study that would pique my interest. While Delft allowed me to learn more than I could have ever hoped about all fields of astronautical engineering, none captivated my imagination quite like laser-thermal propulsion. I was thus excited to have the opportunity to return to my alma mater to kick-off laser-sustained plasma and laser-thermal propulsion experiments at McGill. Although the results of this project are a little different from what I had first (perhaps too ambitiously) envisioned, I am proud of the progress made within a year, and I am confident that my work will provide a valuable base that future students can build upon.

    My name may be alone on the cover page, but this thesis could not have been completed without the valuable support of my mentors, my colleagues, my friends, and my family. I would first like to thank Andrew Higgins, who provided all the guidance and support I could have hoped for, both during my undergraduate studies and this thesis project. Thank you to Barry Zandbergen for supervising me through this project and providing valuable insight and comments which greatly improved the quality of this thesis. Thank you to all the attendees of my midterm review, who all provided useful advice on this project's modeling and experimental work. Thank you to my parents, who have done their best to support me during my studies and especially while writing this report. Thank you to John Kokkalis for offering your apparatus for this experiment. I also want to thank all the students of the Interstellar Flight Experimental Research Group (and a few other labs) for making all of this experience not only enjoyable but also memorable---I would likely have lost my mind otherwise. Last but not least, I want to thank Gabriel and Siera for their hands-on help and for putting up with me for months. I could not have asked for better research partners, and I hope you take this project beyond all our expectations.

    As I write these lines, Gabriel is hard at work preparing a conference presentation (cited below) on the work discussed here. Good luck!

    \fullcite{dubeLaserSustainedPlasmaDeep2024}
    \end{refsection}
\end{plainchp}